Goals:

- Write wrapper functions
- Understand the tradeoffs with different styles of coding

123 GO – What's one item on your Christmas wish list?


## Wrapper functions

Suppose I want to take an existing function and modify it slightly, say by giving the function arguments different defaults.
For example, `pnorm` calculates the cumulative distribution function for the normal distribution:

```{r}
x = seq(from = -4, to = 4, by = 0.1)

```


I want to create a function `pnorm2` that behaves just like `pnorm`, but has the default standard deviation (sd) set to 2.
In other words, `pnorm2(x)` should behave exactly like `pnorm(x, sd = 2)`.
How can I do this?


## Group activity

1. Write a wrapper for `hist` that changes the default title (parameter `main`) to "HISTOGRAM".
2. List the differences between the functions `extract_interest_rate` and `eir` in https://github.com/clarkfitzg/stat128/blob/master/extract_interest.R


## Debugging

References:

- [Debugging in Advanced R](http://adv-r.had.co.nz/Exceptions-Debugging.html)
- [Debugging with Rstudio](https://support.rstudio.com/hc/en-us/articles/200713843?version=1.3.1073&mode=desktop)

If you want to be a good software developer, then learn to debug.

What's a bug in software?

Four kinds of bugs:




## Errors

The following function from our course Discord history contains at least one error:

```{r}
high = function (x)
{
    win = (x > 18 = 0) & (!x = 0)
    ifelse(win, 1, -1)
}

high(0:36)
```

When we try to run it, we see a mysterious error: `Error in x > 18 = 0 : could not find function "><-"`.
This message tells us exactly where the problem is.
Where is it? 
The expression `x > 18 = 0`.


123 GO - Is this a syntax or a runtime error?
Runtime, unfortunately.

```{r}
x = 1:3
x[1] = 0

# equivalently:
x = `[<-`(x, 1, 0)
```



## Debugging


## Write code that's easy to understand


```{r}
#' Extract interest rates from a character vector
#'
#' @param x character vector containing text with interest rates
#' @param pattern regular expression pattern to find the matching interest rates
#' @return The first numeric interest rate found in the string, or NA if none found
#' @examples
#' extract_interest_rate("Fixed @ 3.92%, no TIC/NIC")  # 3.92
#' extract_interest_rate("123.456 but no adjacent %")  # NA
extract_interest_rate = function(x, pattern = "[0-9]+\\.[0-9]+\\%")
{
    interest = rep(NA, length(x))
    match_locations = regexpr(pattern, x)
    match_string = regmatches(x, match_locations)
    match_number_string = gsub("\\%", "", match_string)
    match_number = as.numeric(match_number_string)
    interest[match_locations != -1] = match_number
    interest
}


eir = function(x, p = "[0-9]+\\.[0-9]+\\%")
{
    i = rep(NA, length(x))
    l = regexpr(p, x)
    n = as.numeric(gsub("\\%", "", regmatches(x, l)))
    (i[l != -1] = n)
}
```

These 
What are the differences between these functions?

Which version of this function is easier to read?
